Remark on the hypothetical judgment

### 2015-08-01 paper.tex
cite pml's axiom of choice paper

The judgments and demonstrations are the activity of the subject in performing
and experiencing mathematics. On the other hand, the theory of sets that we have
defined is, to my mind, the correct level at which to \emph{do} mathematics,
where objects are concrete and have an extensional identity. By guaranteeing
pervasive functionality, we have embedded in the rich world of intuitionistic
mathematics a haven invulnerable to the paradoxes that arise from failures of
extensionality, such as Diaconescu's theorem \cite{sterling:diaconescu}.

>>>>

The judgments and demonstrations are the activity of the subject in performing
and experiencing mathematics. On the other hand, the theory of sets that we have
defined is, to my mind, the correct level at which to \emph{do} mathematics,
where objects are concrete and have an extensional identity. By guaranteeing
pervasive functionality, we have embedded in the rich world of intuitionistic
mathematics a haven invulnerable to the paradoxes that arise from failures of
extensionality, such as Diaconescu's theorem \cite{martin-lof:2009, sterling:diaconescu}.
